---
title: "Class10"
author: "Elaine Schaft"
date: "2026-03-04"
output: html_document
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidy Data with Built-In Data from 'tidyr'

## 'table1'

```{r}
tidyr::table1
```

'table1' is tidy since:

- every row corresponds to a single obs (out unit of analysis is country-year);
- every col corresponds to one of the four variables we have in the dataset

## 'table2'

```{r}
tidyr::table2
```

'table2' is **NOT** tidy since:

- Our country-year (unit of analysis) shows in two different rows
- our 'type' column contains two different variables

To fix this, what we would like to do is to take that type column and distribute it into two columns.

```{r}
table2_not_tidy = tidyr::table2

# Fix: making the dataset "wider" [you will lose half your rows]
table2_tidy_df = tidyr::pivot_wider(
  data = table2_not_tidy,  # untidy data
  names_from = type, # names of the new columns should come from type
  values_from = count # values for these two additional cols should come from "count" col
)

# Note that this looks exactly like table1
table2_tidy_df
```

## 'table3'

```{r}
tidyr::table3
```

'table3' is not tidy since the rate column contains two variables. We will want to **separate** the two variables into their own columns. This separation is going to leverage the '/'.

```{r}
table3_untidy = tidyr::table3

tidyr::separate(
  data = table3_untidy, # df that has column that needs to be separated
  col = rate, # this is the name of the col
  into = c("cases", "population"), # the two new cols that we created
  sep = "/" # this is optional; the original separator works well since it uses anything that is not a number or a chr to split on
  )

```

## 'table4a' and 'table4b'

```{r}
tidyr::table4a
```

```{r}
tidyr::table4b
```

These are both not tidy since the year variable is split into different cols. We violate the rule that each variable has to be in 1 column.

```{r}
tidyr::table4a # not tidy and we want to make this "longer"

table4a_tidy = tidyr::pivot_longer(
  data = tidyr::table4a, # since I did not save it
  cols = 2:3, #c(2, )
  names_to = 'year',
  values_to = 'cases'
)
```


```{r}
tidyr::table4b # not tidy and we want to make this "longer"

table4b_tidy = tidyr::pivot_longer(
  data = tidyr::table4b, # since I did not save it
  cols = '1999':'2000', # backticks are needed since R does not like var to start with a number
  names_to = 'year',
  values_to = 'population'
)
```

```{r}
# So in 345, how would you have combined the two tables together"
table4_tidy = dplyr::left_join(x = table4a_tidy, y = table4b_tidy, by = c("country", "year"))

# for technically correct data, all columns should have the correct class/data type
table4_tech_correct = 
  table4_tidy |>
  dplyr::mutate(
    year = as.numeric(year) # converted from chr (saw from printing out the tibble) into a number
  )
```

```{r}
## consistent data: "on the cell level, where we are making sure that the values are correct and we have no missing data [typically; depending on how you analyze the data]" -> clean dataset
```

