---
title: "Class 06 - Scraping Webpages (cont.)"
author: "Elaine Schaft"
date: "2026-02-23"
output: html_document
  toc: TRUE
  toc_float: TRUE
  number_sections: TRUE
  code_folding: show
  code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Demo 1: Scrapign the Miami University ISA Course Bulletin

My goal is to scrape every course in [MU ISA Course Bulletin](https://bulletin.miamioh.edu/courses-instruction/isa/)

```{r mu_isa}
# Step 0: check robots.txt
cat("Based on the robotstxt package, I checked the path and I found that I am allowed to scrape the page. This is illustrated by the output being TRUE.")
  
robotstxt::paths_allowed(
  paths = "https://bulletin.miamioh.edu/courses-instruction/isa/"
)

# Step 1: Get the HTML into R
mu_bulletin_page = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# Steps 2 and 3: get the titles and descriptions and save them  in separate objects
mu_bulletin_page |>
  # I removed the nth-child() becuase I wanted to get all the courses
  # alternitively, I could have used p.courseblocktitle > strong OR even just strong
  rvest::html_elements("#sc_sccoursedescs > div > p.courseblocktitle > strong") |>
  rvest::html_text2() -> course_titles

mu_bulletin_page |>
  rvest::html_elements(".courseblockdesc") |>
  rvest::html_text2() -> course_descs

mu_bulletin_page |>
  rvest::html_elements("div p") |>
  rvest::html_text2() -> test_results

# if you started with a sub optimal selector, you can work your way to the
# correct final answer as illustrated below
test_results = test_results[1:100] # which contained print, pdf related things
tail(test_results)

course_titles_c = test_results[ seq(from = 1, to = 100, by = 2)]
course_descs_c = test_results[ seq(from = 2, to = 100, by = 2)]

isa_course_df = data.frame(
  title = course_titles, description = course_descs
)
```


## A function to scrape other FSB courses

```{r my_function}
# Based on the first answer in class, we decided to use the suffix of the URL
# e.g., for https://bulletin.miamioh.edu/courses-instruction/isa/
# we can use: (a) /isa/, (b) isa/, or (c) just isa [won based on first answer]
# all answers are equally reasonable
scrape_fsb_courses = function(suffix = 'isa'){
  fsb_url = paste0("https://bulletin.miamioh.edu/courses-instruction/", suffix, "/")
  
  # note that we used the variable created in the previous step so the URL can change
  # if you names it like what we had before, you can copy your previous code
  mu_bulletin_page = rvest::read_html(fsb_url)
  
  mu_bulletin_page |>
  # I removed the nth-child() becuase I wanted to get all the courses
  # alternitively, I could have used p.courseblocktitle > strong OR even just strong
  rvest::html_elements("#sc_sccoursedescs > div > p.courseblocktitle > strong") |>
  rvest::html_text2() -> course_titles

  mu_bulletin_page |>
  rvest::html_elements(".courseblockdesc") |>
  rvest::html_text2() -> course_descs
  course_descs
  
df = data.frame(title = course_titles, description = course_descs)

# so to be nice we will add a pause so that we do not overwhelm Miami's servers
Sys.sleep(2)

return(df) # this is what the function will do
}
```


## Using out Function: Once

Just to illustrate how the function will be called

```{r use_function_for_finance}
fin_df = scrape_fsb_courses(suffix = "fin")
```

## Using out Function: More than Once

With the DRY principle, we do not want to repeat the call above multiple times. So first we will explore doing that via 'for' loop.

```{r use_function_in_a_for_loop}
fsb_suffix_vec = c('isa', 'fin', 'acc', 'eco', 'esp', 'mgt', 'bus', 'mkt')

fsb_df = data.frame()
for(name in fsb_suffix_vec){
  df = scrape_fsb_courses(suffix = name)
  
  # binding two data frames by rows (i.e., putting them on top of each other)
  fsb_df = rbind(fsb_df, df)
}
```

## Using out Function: More than Once ('purrr')

Instead of a 'for' loop, we will use the 'purrr::map_df()' for looping across the different departments.

```{r purrr}
fsb_suffix_vec = c('isa', 'fin', 'acc', 'eco', 'esp', 'mgt', 'bus', 'mkt')

fsb_df_alt = purrr::map_df(.x = fsb_suffix_vec, .f = scrape_fsb_courses)
```

## Trying it for just one

```{r}
robotstxt::paths_allowed("https://www.planecrashinfo.com/2025/2025.htm")
```


```{r}
plane_url = "https://www.planecrashinfo.com/2025/2025.htm"

# step 1 to get that webpage (raw HTML into R)
plane_webpage = rvest::read_html(plane_url)

# steps 2 and 3 together --> output is to get a "clean" table
plane_webpage |>
  rvest::html_elements("center > table") |>
  rvest::html_table(header = TRUE) |>
  magrittr::extract2(1) ->
  df
```

## Our Own Scraping Function

```{r scrape_crashes}
crash_urls = paste0("https://www.planecrashinfo.com/", 2025:2026, "/", 2025:2026, ".htm")

scrape_crashes = function(plane_url){

  Sys.sleep(2)

  plane_webpage = rvest::read_html(plane_url)

  # steps 2 and 3 together --> output is to get a "clean" table
  plane_webpage |>
    rvest::html_elements("center > table") |>
    rvest::html_table(header = TRUE) |>
    magrittr::extract2(1) -> df
  
return(df)
}
```

## Apply My Function to Multiple Years

```{r scrape_mult_yrs}
crash_urls = paste0("https://www.planecrashinfo.com/", 2025:2026, "/", 2025:2026, ".htm")

crash_df = purrr::map_df(.x = crash_urls, .f = scrape_crashes)
```

## Google Careers Scraping

A note on 'robotstxt'
```{r}
# returns False
robotstxt::paths_allowed(paths = "https://www.google.com/about/careers/applications/jobs/results/?q=data%20analyst&location=United%20States&page=1")

# returns TRUE
robotstxt::paths_allowed(domain = "https://www.google.com/about/",
                         paths = 'careers')

# By Inspecting the actual robots.txt, we realized that we should not scrape this but we will TRY to do it for the purpose of a class

google_url = "https://www.google.com/about/careers/applications/jobs/results/?q=%22business%20analyst%22&location=United%20States&target_level=MID&target_level=EARLY&target_level=INTERN_AND_APPRENTICE"

google_page = rvest::read_html(google_url)

google_page |> rvest::html_elements("h3") |> rvest::html_text2() -> titles

google_page |> rvest::html_elements("div > span.pwO9Dc.vo5qdf > span:nth-child(2)") |> rvest::html_text2() -> first_location
```

