---
title: "Class 02: R Basics"
author: "Elaine Schaft"
date: "2026-02-02"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Operators

In R, there are three assignment operators:  

  -  '->',
  -  '=' and,
  -  '<-',
  
For example:

```{r}
x1 = 5
5 -> x3
```

## Atomic Vectors

You can think of an atomic vector as a col of data in Excel. However, it can only take a single data type, which means that if you combined multiple data types in it, it will return the most general class.

```{r atomic_vectors}
mixed_vec1 = c('ISA', 401L) # this will return a chr vector

mixed_num = c(401L, 3.14) # typeof(mixed_num) returns a double (more general than an integer)
```

## Lists

Lists are very felxible as they can have different datasets within it

```{r}
lst <- list( # list constructor/creator
 1:3, # atomic double/numeric vector  of length = 3
 "a", # atomic character vector of length = 1 (aka scalar)
 c(TRUE, FALSE, TRUE), # atomic logical vector of length = 3
 c(2.3, 5.9) # atomic double/numeric vector of length =3
)
lst # printing the list

sublist = lst[1]
```



