---
title: "HW5"
author: "Elaine Schaft"
date: "2026-03-06"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read the data
```{r}
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, magrittr, magrittr, readxl, hms)

df <- readxl::read_xlsx("sample_shimmer.xlsx")
head(df)
```
some people may consider df not tidy due to the first column (i.e., `Shimmer_B663_Timestamp_FormattedUnix_CAL (yyyy/mm/dd hh:mm:ss.000)`) since it contains both date and time. Others would argue that this is just part of the time being a continuum. 

## would this create a new column titled date in the data of class Date?
```{r}
df$date = lubridate::as_date(  df$`timestamp (yyyy/mm/dd hh:mm:ss.000)`  ) 

class(df$date)
# head(df$date)
```
yes, this would create a new column of class Date


## would this create a new column titled time in the data of class hms? Hint: check the output from the class().
```{r}
df$time = hms::as_hms( df$`timestamp (yyyy/mm/dd hh:mm:ss.000)` )

class(df$time)
head(df$time)
```
This creates a new column called time of class hms.

## T OR F
If you were to delete the first column, i.e., setting, Now the df object can be considered tidy.
```{r}
df$`timestamp (yyyy/mm/dd hh:mm:ss.000)` = NULL
```
TRUE
